\documentclass{article}

\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{geometry}
\usepackage{caption}
\usepackage{indentfirst}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{minted}
\usemintedstyle{autumn}
\setminted{linenos,breaklines,tabsize=4,xleftmargin=1.5em}
\geometry{left=3.0cm,right=3.0cm,top=3.0cm,bottom=4.0cm}
\title{VG496 Case Study Homework 1}
\author{Liu Yihao 515370910207}
\date{}

\begin{document}
\maketitle

\section{List as many ethical issues as possible}

\begin{enumerate}
\item Should Wang take care of his parents or pay more attention on work?
\item Should Wang report the heating issue to the supervisor Lu?
\item Should Lu give Wang more time on the heating issue?
\item Should Lu follow the advice of the management of Kitten to make the heater available before all issues solved?
\item Should Kitten keep the information of financial difficulties from the employees?
\item Should Lu release the products with heating issue and recall them later?
\item Should Wang follow the advice of Lu to ignore this issue now?
\end{enumerate}

\section{Choose the most important one}

The most important one is ``Should Wang follow the advice of Lu to ignore this issue now?''. I think it is the final question in this case, Wang should consider many other things, like family, supervisor, the company and etc., except from engineering ethics before making the decision.

\section{List facts that would help to resolve the most important issue/answer the question as well as identifying any relevant missing facts}

Facts:

\begin{itemize}
\item Wang's parents are not able to work and his work is the only financial source of the family.
\item The products Wang is working on is for people in situation similar to him, he wants to ensure their safety.
\item The company is in financial difficulties and a rival company will release similar products after a month scheduled by Kitten so that Kitten needs to sell products as soon as possible. 
\item The heating issue is rare and is found when the product works for a long time.
\item Wang's supervisor Lu wants him to skip the issue and recall the products if problems found later.
\end{itemize}

Missing Facts:

\begin{itemize}
\item Whether the promise of Lu's recall correction can be realized.
\item Whether Wang will lose his job if he doesn't take Lu's advice.
\item Whether the company will bankrupt if the products can't be sold soon, and Wang, Lu and many others will all lose job because of that.
\end{itemize}

\section{Make reasonable assumptions regarding missing facts}

Since Lu seems lacking of engineering ethics, if the products sells very well and profits a lot, he may refused to recall them later. \\

If Wang refused Lu's suggestions, Lu may substitute him with someone else to deal with the problem and release the product on time \\

If finally they don't release the product on time, the financial problem of Kitten will become worse. So it is very likely that all of them will lose job.

\section{Clarify the use of any potentially ambiguous terminology you've used so far}

Rare: about one out of one thousand. \\

A long time: 2000 hours.



\end{document}